---
title: "MappingTopTen"
author: "Tim Gabriel"
date: "2024-04-28"
output: html_document
---

```{r, echo=FALSE}
library(GDELTtools)
library(dplyr)
library(urltools)
library(readxl)
library(tidyr)
library(rvest)
```

#Dataset for one date
```{r}
apr29 <- GetGDELT("2024-04-29")
apr29
```

# group_by to separate into events
# sum mentions, keep lists of URLs with tones
# arrange by number of mentions
# keep top ten events
```{r}
apr29 %>%
  group_by(EventCode,Actor1Geo_Lat,Actor1Geo_Long,ActionGeo_Lat,ActionGeo_Long) %>%
  summarize(mentions=sum(NumMentions), tone = list(AvgTone), URLs = list(SOURCEURL), .groups="drop") %>%
  arrange(desc(mentions)) %>%
  select(EventCode,URLs,tone) %>%
  slice_head(n=10) %>%
  mutate(index=c(1,2,3,4,5,6,7,8,9,10)) %>%
  select(index, URLs, tone) %>%
  unnest(c(URLs,tone)) %>%
  mutate(domain = (domain(URLs))) -> topTen
topTen
```

# Join with wikipedia list of country web domains
```{r}
countryDomains <- read_excel("countryDomains.xlsx")
topTen %>% 
  mutate(suffix = sub(".+\\.", ".", domain)) %>%
  left_join(countryDomains, by = c("suffix"="domain")) -> df2
df2
```
# Removing NAs makes list much shorter

```{r}
df2 %>% na.omit() -> urlList
urlList
```
# Pick out event with most mentions
# group_by country
# keep list of URLs and find average tone in each country
# sort by average tone
```{r}
urlList %>% 
  filter(index==1) %>%
  group_by(country) %>%
  summarize(URLs = list(URLs), meanTone=mean(tone) , .groups="drop") %>%
  arrange(desc(meanTone)) -> df3
df3
```
# To investigate URLs choose max and min tone
# Show URLs
```{r}
df3 %>%
  slice(n()) %>%
  bind_rows(df3 %>% slice(1)) %>%
  unnest(URLs) -> df4
df4
```
# Function to pull webpage html title
# apply this function to URLs
```{r}
get_html_title <- function(url) {
  webpage <- read_html(url)
  title <- html_text(html_node(webpage, "title"))
  return(title)
}
df4 %>%
  mutate(title = lapply(URLs, get_html_title)) %>%
  unnest(title) %>%
  select(country, title)
```
# Map tones by country
```{r fig.width=10}
library(sf)
library(ggplot2)
worldShapeFiles <- read_sf("TM_WORLD_BORDERS_SIMPL-0.3.shp")

#Manual editing may be necessary for some country names
#df3 %>%
#  mutate(country = replace(country, 1, "Iran (Islamic Republic of)")) %>%
#  mutate(country = replace(country, 2, "China")) %>%
#  mutate(country = replace(country, 4, "United States")) -> df3

worldShapeFiles %>%
  left_join(df3, by = c("NAME"="country")) -> df5

ggplot(df5) +
  geom_sf(aes(fill=meanTone)) +
  scale_fill_distiller(palette="Reds",direction=1, name="",na.value="gray") +
  labs(title="Average Tone by Country")+
  theme_void()
```